\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours

### 2021-11-15 manuscript.Rmd
* Semantic Scale Network added

For our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one making it a 5 point Likert type response scale. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. 
We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample. Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal]. Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability. In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`. All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`. Items under this factor commonly investigated an individual's hours spent outdoor. The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance. Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed. The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`. The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`. These five items investigated the behaviors related to individual's light exposure before bedtime. Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance. This factor  captured individual's morning and daytime light exposure related behavior.  The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` . It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items. Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA scale for both the EFA and CFA sample.

@@

```{r mod2, include=FALSE}
modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
modfit.Cor.one[modfit.Cor.one$mi>3.84,]
```
We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018]. Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015]. Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR). Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit. Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the $\chi^2$ test. However, the $\chi^2$ test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015]. Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272]. We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 . However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999. 
Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega$ (total) coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. McDonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.

@@

## Measurement Invariance
Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**. Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring]. Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. 
The invariance model fit of our scale was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999]. We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272]. Table \@ref(tab:InvarianceTab) summarized the fit indices. The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI. A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

@@

## Developing Short form of LEBA

We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our scale. Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.

@@

Test information curve (TIC) (Figure \@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \@ref(Fig:Testinfo)). These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)). Also the amount of information changed rather steadily with the change of ($\theta$). Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

>>>>

For our analysis we used R (version 4.1.0), with several R packages. Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always). Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information. As such we decided to collapse them into one making it a 5 point Likert type response format. Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed. Our data violated both the univariate and multivariate normality assumptions. Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA. We employed principal axis (PA) as  factor extraction method with varimax rotation. PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020]. The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well. We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers. Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]. 
We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.

@@

Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample. Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal]. Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability. In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`. All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments. The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`. Items under this factor commonly investigated an individual's hours spent outdoor. The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance. Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed. The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`. The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`. These five items investigated the behaviors related to individual's light exposure before bedtime. Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance. This factor  captured individual's morning and daytime light exposure related behavior.  The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` . It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure. As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA). Two items showed negative factor-loading (items 44 and 21). Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items. Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.

@@

```{r mod2, include=FALSE}
modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
modfit.Cor.one[modfit.Cor.one$mi>3.84,]
```
We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018]. Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015]. Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR). Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model. Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero. Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices. Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit. Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model. Our fitted model failed to attain an absolute fit estimated by the $\chi^2$ test. However, the $\chi^2$ test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015]. Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272]. We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA. Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`]. Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime. Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`). Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999. 
Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively. We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega$ (total) coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. McDonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.

@@

## Measurement Invariance
Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015]. We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**. Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring]. Among these nested models  configural model is the first and least restrictive model. The configural model assumes that the number of factors and item number under each factor will be equal across two groups. The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal. Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently. Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups. This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups. The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups. This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs. 
The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999]. We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272]. Table \@ref(tab:InvarianceTab) summarized the fit indices. The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI. A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted. We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons. Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models. The model fit did not significantly decrease across the nested models up to the scalar MI model. The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.

@@

## Sementic Analysis 
To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis[@rosenbusch2020semantic]. The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy. LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51. Two factors of our LEBA tool: "Using phone and smart-watch in bed" and "Using light before bedtime" dealt with light exposure related behavior pertaining to sleep quality. As such the similarity index obtained is expected.

## Developing Short form of LEBA
We sought the item response theory (IRT) to develop the short form of LEBA. IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017]. IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$). We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690). Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA. @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70. Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool. Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$). Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.

@@

Test information curve (TIC) (Figure \@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum. As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \@ref(Fig:Testinfo)). These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)). Also the amount of information changed rather steadily with the change of ($\theta$). Thus we conferred the LEBA tool (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor. The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
